Title

### 2014-01-16 paper/parts/results.tex
Fixed figure. Fixed a few minor typos.

For example, Figure~\ref{Fig-edge_types} shows the distributions of hashtag-based weights for the largest community defined by the mention-retweet network. We see that the distribution of internal-to-internal hashtag weights has a longer tail than either the external-to-internal or internal-to-external hashtag weights, with edges within the community having higher weights than edges crossing the boundary of the community. Thus, while the community was defined in terms of interactions, we still see a shift in the distribution of \emph{topic-similarity}.

@@

>>>>

For example, Figure~\ref{Fig-dist_across_community} shows the distributions of hashtag-based weights for the largest community defined by the mention-retweet network. We see that the distribution of internal-to-internal hashtag weights has a longer tail than either the external-to-internal or internal-to-external hashtag weights, with edges within the community having higher weights than edges crossing the boundary of the community. Thus, while the community was defined in terms of interactions, we still see a shift in the distribution of \emph{topic-similarity}.

@@

\subsection{Qualitative Analysis}

In order to further explore the differences between the communities obtained through the various weightings, we also performed a qualitative analysis of such communities. Some interesting examples are, for instance, communities in the topic-based network such as one composed of 83 users who talk about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability, and another one 47 users talking about small businesses and entrepreneurship, characterized by hashtags such as \#smallbiz, \#marketing and \#enterpreneur. In both cases most members of the topic-based communities are not found in the same community in the other networks, indicating that these people talk about the same things and can therefore be considered a thematic community, but do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior. Another interesting example is the one of a community thematically focused on Denver and Colorado, whose users do not belong to the same community in the interaction networks, but most of them do belong to the same community in the information based network. This indicates that these users react on the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and in the activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
